### 2016-03-24 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Removed section of gas fire experiment report so .tex can compile again
Fixed compile error in .tex file for gas fire experiment report
Updated east exp times/description for gas fire exp report

This report describes eight full-scale fire experiments in which the effects of changing the ventilation patterns within a structure were studied. The experiments were conducted in two structures designed to replicate typical residential dwellings. During each test, propane was provided to three diffusion flame burners at a measured flow rate. Local measurements of temperature, gas velocity, heat flux, and gas concentrations were collected at various locations throughout the structure while ventilation patterns within the structure were changed by opening and closing certain doors and vents.

@@

\section{East Structure Tests}
\label{sec:east_procedure}
Four different tests---Test 2, Test 3, Test 4, and Test 5---were conducted in the East Structure. Each series was composed of three experiments that used an identical procedure to change the ventilation in the structure. The experiments conducted during Series 4 followed a procedure in which each exterior door was opened to change the ventilation pattern. During the experiments in Series 5, each double door was opened and the roof vent was opened and closed. Both the roof vent and west double door were opened during each experiment in Series 6. Figs.~\ref{fig:east_test_4}--\ref{fig:east_test_6} include a schematic and additional details about the procedures used for the experiments during Series 4--6.

% \begin{table}[!ht]
% \caption{Event times for Tests 2-4}
% \begin{tabular}{lccc}
% \toprule
%  & \multicolumn{3}{c}{\textbf{\underline{Event Time (mm:ss)}}} \\
% \textbf{Event} 				& \textbf{Test 2} & \textbf{Test 3} & \textbf{Test 4} \\
% \midrule
% Corner burner on 			& 	21:00		  &		4:00		&		4:00	  \\
% Middle burner on 			&   24:00		  &		7:00		&		7:00	  \\
% Center burner on 			&   27:00		  &	   10:00		&	   10:00	  \\
% West double door opened 	&   28:00		  &    11:00		&	   11:00	  \\
% East double door opened 	&   30:00		  &    13:00		&	   13:00	  \\
% South exterior door opened 	&   31:00		  &    14:00		&	   14:00	  \\
% Center burner off 			&   33:00		  &    17:00		&	   17:00	  \\
% Middle burner off 			&   35:00		  &    19:00		&	   19:00	  \\
% Corner burner off 			&   37:00		  &    21:00		&	   21:00	  \\
% \bottomrule
% \end{tabular}
% \label{table:Tests_2-4_times}
% \end{table}
% RAN FAN AFTER BURNER WAS OFF, BUT DIDN'T INCLUDE BECAUSE BURNERS WERE OFF

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\small
	\begin{tabular}{lccc}
\multicolumn{4}{c}{\normalsize Event Times (mm:ss) for Test Data File} \\
\toprule
\multicolumn{1}{c}{\textbf{Event}} & \textbf{Test 2} & \textbf{Test 3} & \textbf{Test 4} \\
\midrule
(1) Corner burner on 			& 	21:00		  &		4:00		&		4:00	  \\
(2) Middle burner on 			&   24:00		  &		7:00		&		7:00	  \\
(3) Center burner on 			&   27:00		  &	   10:00		&	   10:00	  \\
(4) West double door opened 	&   28:00		  &    11:00		&	   11:00	  \\
(5) East double door opened 	&   30:00		  &    13:00		&	   13:00	  \\
(6) South exterior door opened 	&   31:00		  &    14:00		&	   14:00	  \\
(7) Center burner off 			&   33:00		  &    17:00		&	   17:00	  \\
(8) Middle burner off 			&   35:00		  &    19:00		&	   19:00	  \\
(9) Corner burner off 			&   37:00		  &    21:00		&	   21:00	  \\
\bottomrule
\end{tabular}
	% \begin{tabular}[b]{cc}
 % 	\toprule
 % 	\textbf{Number} & \textbf{Event Description} \\
 % 	\midrule
 % 	1-3  & Burners ignited \\
 % 	4	 & West double door opened \\
 % 	5 	 & East double door opened \\
 % 	6	 & South exterior door opened \\
 % 	7-9  & Burners extinguished \\
	% \bottomrule
	% \end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_4}
\end{minipage}
\caption{Test 2-4 layout and sequence of events.}
\label{fig:Tests_2-4_layout}
\end{figure}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\small
\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\small
	\begin{tabular}{lccc}
\multicolumn{4}{c}{\normalsize Event Times (mm:ss) for Test Data File} \\
\toprule
\multicolumn{1}{c}{\textbf{Event}} & \textbf{Test 2} & \textbf{Test 3} & \textbf{Test 4} \\
\midrule
(1) Corner burner on 			& 	14:00		  &	   34:30		&	   54:30	\\
(2) Middle burner on 			&   14:15		  &	   34:45		&	   54:45	\\
(3) Center burner on 			&   14:30		  &	   35:00		&	   55:00	\\
(4) Roof vent opened 			&   16:38		  &    36:30		&	   56:30	\\
(5) West double door opened 	&	17:03		  &	   38:00 		&	   58:00 	\\
(6) East double door opened 	&   20:03		  &    39:30		&	   59:31	\\
(7) Roof vent closed		 	&   21:30		  &    42:45		&	   61:43	\\
(7) Center burner off 			&   23:00		  &    44:15		&	   63:30	\\
(8) Middle burner off 			&   23:20		  &    44:30		&	   63:45	\\
(9) Corner burner off 			&   23:40		  &    44:45		&	   64:00	\\
(10) Roof vent opened			& 	26:05 		  &	   45:30		&	   65:30	\\
(11) East double door closed	& 	33:17 		  &	   52:38		&	   N/A	\\
(12) West double door closed	& 	33:30 		  &	   52:55		&	   N/A	\\
(13) Roof vent closed		 	&   33:45		  &    53:54		&	   N/A	\\
\bottomrule
\end{tabular}

	% \begin{tabular}[b]{cc}
 % 	\toprule
 % 	\textbf{Number} & \textbf{Event Description} \\
 % 	\midrule
 % 	1-3  & Burners ignited \\
 % 	4	 & Roof vent opened \\
 % 	5 	 & West double door opened \\
 % 	6 	 & East double door opened \\	
 % 	7	 & Roof vent closed \\
 % 	8-10  & Burners extinguished \\
	% \bottomrule
	% \end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_5}
\end{minipage}
\caption{Test Series 5 layout and sequence of events.}
\label{fig:east_test_5}
\end{figure}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\small
	\begin{tabular}[b]{cc}
 	\toprule
 	\textbf{Number} & \textbf{Event Description} \\
 	\midrule
 	1-3  & Burners ignited \\
 	4	 & Roof vent opened \\
 	5 	 & West double door opened \\
 	6-8  & Burners extinguished \\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_6}
\end{minipage}
\caption{Test Series 6 layout and sequence of events.}
\label{fig:east_test_6}
\end{figure}
\FloatBarrier

>>>>

This report describes nine full-scale fire experiments in which the effects of changing the ventilation patterns within a structure were studied. The experiments were conducted in two structures designed to replicate typical residential dwellings. During each test, propane was provided to three diffusion flame burners at a measured flow rate. Local measurements of temperature, gas velocity, heat flux, and gas concentrations were collected at various locations throughout the structure while ventilation patterns within the structure were changed by opening and closing certain doors and vents.

@@

\section{East Structure Tests}
\label{sec:east_procedure}
Five different tests---Test~2, Test~3, Test~4, Test~5, and Test~6---were conducted in the East Structure. Tests~2--4 followed an identical order of events. Fig.~\ref{fig:Tests_2-4_layout} includes a floor plan schematic and table of event times corresponding to the data files for Tests~2--4. The procedures for Test~5 and Test~6 are outlined in a similar manner in Fig.~\ref{fig:east_test_5} and Fig.~\ref{fig:east_test_6}, respectively. Tests~5 and 6 involved performing a specific set of events three times sequentially. To avoid repetition of identical actions in the event time table, each set of events has been denoted as a ``sequence'' (abbreviated as ``seq.'' in the table).

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\small
	\begin{tabular}{lccc}
	\multicolumn{4}{c}{\normalsize Event Times (mm:ss) for Test Data File} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} & \textbf{Test 2} & \textbf{Test 3} & \textbf{Test 4} \\
	\midrule
	(1) Corner burner on 			& 	21:00		  &		4:00		&		4:00	  \\
	(2) Middle burner on 			&   24:00		  &		7:00		&		7:00	  \\
	(3) Center burner on 			&   27:00		  &	   10:00		&	   10:00	  \\
	(4) West double door opened 	&   28:00		  &    11:00		&	   11:00	  \\
	(5) East double door opened 	&   30:00		  &    13:00		&	   13:00	  \\
	(6) South exterior door opened 	&   31:00		  &    14:00		&	   14:00	  \\
	(7) Center burner off 			&   33:00		  &    17:00		&	   17:00	  \\
	(8) Middle burner off 			&   35:00		  &    19:00		&	   19:00	  \\
	(9) Corner burner off 			&   37:00		  &    21:00		&	   21:00	  \\
	\bottomrule
	\end{tabular}
	\\~\\
	\textit{We ran a PPV fan after each test, but I didn't include it because the burners were off at the time. I can include this event if you would like, however. Unlike Tests 5 and 6, we did not ignite the burners again after running the PPV fan.}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_4}
\end{minipage}
\caption{Tests~2-4 layout and event times.}
\label{fig:Tests_2-4_layout}
\end{figure}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\small
	\begin{tabular}{lccc}
	\multicolumn{4}{c}{\normalsize Event Times (mm:ss) for Test Data File} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} & \textbf{Seq. 1} & \textbf{Seq. 2} & \textbf{Seq. 3} \\
	\midrule
	(1)  Corner burner on 			&	3:15	&	12:45	&	21:15	\\
	(2)  Middle burner on 			&	3:30	&	13:00	&	21:30	\\
	(3)  Center burner on 			&	3:45	&	13:15	&	21:45	\\
	(4)  West double door opened 	&	5:15	&   14:45	&	23:15	\\
	(5)  Roof vent opened 			&	6:45	&	15:45 	&	24:45 	\\
	(6)  Center burner off 		 	&	8:15	&   17:15	&	\multirow{3}{*}{Gas killed at truck (26:15)} \\
	(7)  Middle burner off		 	&	8:30	&   17:30	&	\\
	(8)  Corner burner off 			&	8:45	&   17:45	&	\\
	(9)  East double door opened	&	9:30	&   18:30	&	27:25	\\
	(10) Roof vent closed 			&	11:35	&   20:11	&	N/A		\\
	(11) East double door closed	&	12:02 	&	20:24	&	N/A 	\\
	(12) West double door closed	&	12:18 	&	20:41	&	N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_5}
\end{minipage}
\caption{Test~5 layout and event times.}
\label{fig:east_test_5}
\end{figure}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\small
	\begin{tabular}{lccc}
	\multicolumn{4}{c}{\normalsize Event Times (mm:ss) for Test Data File} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} & \textbf{Seq. 1} & \textbf{Seq. 2} & \textbf{Seq. 3} \\
	\midrule
	(1) Corner burner on 			& 	14:00		  &	   34:30		&	   54:30	\\
	(2) Middle burner on 			&   14:15		  &	   34:45		&	   54:45	\\
	(3) Center burner on 			&   14:30		  &	   35:00		&	   55:00	\\
	(4) Roof vent opened 			&   16:38		  &    36:30		&	   56:30	\\
	(5) West double door opened 	&	17:03		  &	   38:00 		&	   58:00 	\\
	(6) East double door opened 	&   20:03		  &    39:30		&	   59:31	\\
	(7) Roof vent closed		 	&   21:30		  &    42:45		&	   61:43	\\
	(7) Center burner off 			&   23:00		  &    44:15		&	   63:30	\\
	(8) Middle burner off 			&   23:20		  &    44:30		&	   63:45	\\
	(9) Corner burner off 			&   23:40		  &    44:45		&	   64:00	\\
	(10) Roof vent opened			& 	26:05 		  &	   45:30		&	   65:30	\\
	(11) East double door closed	& 	33:17 		  &	   52:38		&	   N/A		\\
	(12) West double door closed	& 	33:30 		  &	   52:55		&	   N/A		\\
	(13) Roof vent closed		 	&   33:45		  &    53:54		&	   N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_6}
\end{minipage}
\caption{Test~6 layout and event times.}
\label{fig:east_test_6}
\end{figure}
\FloatBarrier
